Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-16 paper/paper.tex
move figures

\ml{VL. provide parameters for scattering
\texttt{
case 'scat'
    filt\_opt.Q = [12 1];
    filt\_opt.J = T\_to\_J(sr*setting.sct/1000, filt\_opt);
case 'tfscat'
    tm\_filt\_opt.Q = [12 1];
    tm\_filt\_opt.J = T\_to\_J(sr*setting.sct/1000, tm\_filt\_opt);
    fr\_filt\_opt.J = 4;}}

\begin{figure}
\caption{\csentence{Sample scattering}
Same 3 sounds spec + scatt.
% TODO figure + caption
}
\end{figure}

@@

>>>>

\ml{VL. provide parameters for scattering
\texttt{
case 'tfscat'
    tm\_filt\_opt.Q = [12 1];
    tm\_filt\_opt.J = T\_to\_J(sr*setting.sct/1000, tm\_filt\_opt);
    fr\_filt\_opt.J = 4;}}

@@

\begin{figure}
\caption{\csentence{Sample scattering}
Same 3 sounds spectrogram + scattering
% TODO figure + caption
}
\label{fig:sample-scattering}
\end{figure}
